The imprint of global magma oceans on exoplanet demographics

### 2022-12-20 src/tex/ms.tex
state model parameters for H_MO, H_null

>>>>

\begin{note}
    The only free parameter of the null hypothesis, which assumes the average radius to be independent of instellation, is the predicted mean radius $<R_\mathrm{P}>$.
    The functional form of the magma ocean hypothesis is more complex: Besides the mean radius of planets outside the runaway greenhouse threshold $<R_\mathrm{P}>_\mathrm{out}$, which is a nuisance parameter necessary to define the hypothesis, it relies on the threshold instellation for the ``step'' $S_\mathrm{thresh}$.
    Further, the parameter encoding the amount of radius change is the planetary water mass fraction~$x_{H_2O}$.
\end{note}
